Stability and Chaos in Multi-agent Reinforcement Learning

### 2020-10-19 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex

A point which we wish to discuss here is the difference in the result
found w.r.t.~\cite{Sanders2018}, which considered the stability of
\textit{experience weighted attraction} (EWA). Namely, Sanders et
al.~found that convergence is seen for higher values of $\alpha$,
whereas lower values give rise to chaos, the opposite of what is found
here. The reason for this can be seen in the update equation of
Q-Learning (\ref{eqn::Qupdate}), whereby smaller values of $\alpha$
result in the agent placing a lower weight on the reward received at
each step. As such, lower values of $\alpha$ result in the agent
taking more conservative steps and yields a higher probability of
convergence. In contrast, the update for EWA does not discount the
reward received at all and, instead, only discounts the previous
knowledge of the Q-value based on higher choices of $\alpha$. In
essence, the difference is the fact that Q-Learning discounts new
information by a factor of $\alpha$, whilst EWA does not. Yet, the
difference in stability caused by this change is significant. This
highlights the importance of performing analyses such as the present
work; it allows for a method to analytically compare the difference
between learning algorithms and, for practitioners, ensure that the
appropriate algorithm is chosen for the parameters of their specific
task.

>>>>

A point which we wish to discuss here is the difference in the result
found w.r.t.~\cite{Sanders2018}, which considered the stability of
\textit{experience weighted attraction} (EWA). Namely, Sanders et
al.~observe that convergence is seen for higher values of $\alpha$,
whereas lower values give rise to chaos, the opposite of what is found
here. The reason for this can be seen in the update equation
(\ref{eqn::Qupdate}) for Q-Learning, whereby smaller values of
$\alpha$ result in the agent placing a lower weight on the reward
received at each step. As such, lower values of $\alpha$ result in the
agent taking more conservative steps and yields a higher probability
of convergence. In contrast, the update for EWA does not discount the
reward received and, instead, only discounts the previous
knowledge of the Q-value based on higher choices of $\alpha$. In
essence, the difference is the fact that Q-Learning discounts new
information by a factor of $\alpha$, whilst EWA does not. Yet, the
difference in stability caused by this change is significant. This
highlights the importance of performing analyses such as the present
work; it allows for a method to analytically compare the difference
between learning algorithms and, for practitioners, to ensure that the
appropriate algorithm is chosen for the parameters of their specific
task.
